atlantisom: simulated ecosystem datasets for assessment model performance testing

### 2020-09-17 atlantisom_landingpage.Rmd
remove authors, add credits

---
title: "atlantisom: simulated ecosystem datasets for assessment model performance testing"
author: "Sarah Gaichas, Christine Stawitz, Kelli Johnson, Alexander Keth, Allan Hicks, Sean Lucey, Emma Hodgson, and Gavin Fay"
date: "`r Sys.Date()`"
output:
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
---

@@

>>>>

---
title: "atlantisom: simulated ecosystem datasets for assessment model performance testing"
date: "`r Sys.Date()`"
output:
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
---

@@

## Credits

Sarah Gaichas, Christine Stawitz, Kelli Johnson, Alexander Keth, Allan Hicks, Sean Lucey, Emma Hodgson, and Gavin Fay
